Figures

### 2016-01-05 scripts/figures.Rmd
touched up ROC fixed roc function

}
plot.ex(0.35,0.95,roc.df,example)

pdf("../results/figures/roc.example.pdf")
plot.ex(0.35,0.95,roc.df,example)
dev.off()

@@

sum_roc<-function(x){
  sum.df<-subset(x,category %in% c(TRUE,FALSE),select=c(category,p.val))# get the TRUE and false variant calls and p.vals
  if(length(which(sum.df$category==T))>0){ # filter out cases where there aren't any TP found
    if(length(which(sum.df$category==F))==0){
      sum.df<-rbind(sum.df,data.frame(category=F,p.val=1))
    }  
    roc(sum.df$category~sum.df$p.val,plot=F,CI=T)
  }
}

@@

roc_df.one<-function(roc_analysis,thr){ # get the coordinates and cut offs for all the points in the ROC object
  roc_analysis<-roc_analysis[unlist(lapply(roc_analysis,is.null))==F]
  all<-lapply(roc_analysis,coords,x=thr,input="thr")

@@

@@

ggplot(subset(sum.df,p.val<0.01),aes(x=Phred,y=MapQ,color=category))+geom_point(alpha=0.5)

@@

# Id the variants as T or F 
true_snv<-read.csv("../data/reference/mutant_id.csv",stringsAsFactor=F) # get the T variants
sum.df<-mutate(sum.df,category=mutation %in% true_snv$mutant) # add Column for True and false variants
wt1_mut<-subset(sum.df,Id=="WT1",select=mutation)
wt2_mut<-subset(sum.df,Id=="WT2",select=mutation)

@@

Hiseq.roc<-ggplot(subset(h.roc.df,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1")+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.002));Hiseq.roc

@@

knitr::kable(subset(h.table.df,gc==5))
```

@@

ggplot(subset(sig.df,category %in% c(T,F)),aes(x=Phred,y=MapQ,color=category))+geom_point(alpha=0.5)+geom_hline(yintercept=30)+geom_vline(xintercept=35)+facet_wrap(~gc)

@@

ggplot(subset(h.cut.df,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1")+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.002))

@@

ggplot(subset(sig.cut.df,category %in% c(T,F) & gc==5),aes(x=Read_pos,fill=category))+geom_histogram(position='dodge')

@@

ggplot(subset(h.cut.read.df,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1")+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.002))

@@

ac_freq<-ac_freq+geom_point(data=subset(medians,gc=="5"),mapping=aes(x=exp.freq,y=median),shape=95,size=30)
ac_freq
```

## Figure 5 Lower inputs
### 10^4
```{r,roc_lower_inputs4}
ggplot(subset(h.cut.read.df,gc==4),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1")+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.002))

@@

### 10^3
```{r,roc_lower_inputs3}
ggplot(subset(h.cut.read.df,gc==3),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1")+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.002))

@@

ggplot(dups.roc,aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1")+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.002))

@@

This is so much better than before. Is there really that much variability between runs?

> tables are right but does the ROC make sense?

### Ordinations
```{r,eval=F}
# No wt variants for this work. I'll start with the out of the box data p<0.01

sig.df<-subset(sig.df,category!="wt" & freq.var>0.01 & exp.freq>0.005) # no need to look at the samples were we expect things to be less than 1%

# at this point I'm just taking the counts on the forward direction and assuming that everyone has the same coverage this will be adjusted later to take a subsample

dcast(sig.df,Id~mutation,value.var ="freq.var",fill = 0)->counts

sample.names<-counts$Id
row.names(counts)<-sample.names
counts<-(subset(counts,select=-c(Id)))
vare.dist<-vegdist(counts);vare.dist

NMDS<-metaMDS(vare.dist,trymax = 100)
stressplot(NMDS)

plot(NMDS)
orditorp(NMDS,display="sites",cex=1.25,air=0.01)

cut.read.sig.df<-subset(cut.read.sig.df,category!="wt" & freq.var>0.01 & exp.freq>0.005) # no need to look at the samples were we expect things to be less than 1%

# at this point I'm just taking the counts on the forward direction and assuming that everyone has the same coverage this will be adjusted later to take a subsample

dcast(cut.read.sig.df,Id~mutation,value.var ="freq.var",fill = 0)->counts

sample.names<-counts$Id
row.names(counts)<-sample.names
counts<-(subset(counts,select=-c(Id)))
vare.dist<-vegdist(counts);vare.dist

NMDS<-metaMDS(vare.dist,trymax = 100)
stressplot(NMDS)

plot(NMDS)
orditorp(NMDS,display="sites",cex=1.25,air=0.01)

>>>>

}
plot.ex(0.35,0.95,roc.df,example)
pdf("~/Box Sync/Lab_work/Talks/2016_812/figures/roc.ex.pdf")
plot.ex(0.35,0.95,roc.df,example)
dev.off()

@@

sum_roc<-function(x){
  sum.df<-subset(x,category %in% c(TRUE,FALSE),select=c(category,p.val))# get the TRUE and false variant calls and p.vals
  if(length(which(sum.df$category==T))>0){ # filter out cases where there aren't any TP found
    if(length(which(sum.df$category==F))==0){
      sum.df<-rbind(sum.df,data.frame(category=F,p.val=1))
    }  
    roc(sum.df$category~sum.df$p.val,plot=F,CI=T,direction=">")
  }
}

@@

roc_df.one<-function(roc_anal,thr){ # get the coordinates and cut offs for all the points in the ROC object
  roc_analysis<-roc_anal[unlist(lapply(roc_anal,is.null))==F]
  all<-lapply(roc_analysis,coords,x=thr,input="thr")

@@

pdf("~/Box Sync/Lab_work/Talks/2016_812/figures/miseq_roc.one.sided.pdf")
 miseq.roc
 dev.off()

@@

ggplot(subset(sum.df,p.val<0.01),aes(x=Phred,y=MapQ,color=category))+geom_point(alpha=1)

@@

sum.df<-subset(sum.df,exp.freq>0.001) # remove this to include exp.freq 0.01%
# Id the variants as T or F 
true_snv<-read.csv("../data/reference/mutant_id.csv",stringsAsFactor=F) # get the T variants
sum.df<-mutate(sum.df,category=mutation %in% true_snv$mutant) # add Column for True and false variants
wt1_mut<-subset(sum.df,Id=="WT1",select=mutation)
wt2_mut<-subset(sum.df,Id=="WT2",select=mutation)

@@

Hiseq.roc<-ggplot(subset(h.roc.df,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.002));Hiseq.roc

pdf("~/Box Sync/Lab_work/Talks/2016_812/figures/hiseq.roc.pdf")
Hiseq.roc
dev.off()

Hiseq.roc.4<-ggplot(subset(h.roc.df,gc==4),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.002));Hiseq.roc

pdf("~/Box Sync/Lab_work/Talks/2016_812/figures/hiseq.roc.4.pdf")
Hiseq.roc.4
dev.off()

@@

knitr::kable(subset(h.table.df,gc==5))

knitr::kable(subset(h.table.df,gc==4))
```

@@

mapq_phred.normal<-ggplot(subset(sig.df,category %in% c(T,F) & gc==5),aes(x=Phred,y=MapQ,color=category))+geom_point(alpha=1)+geom_hline(yintercept=20)+geom_vline(xintercept=30)+scale_x_continuous(limits=c(30,40))+scale_color_hue(name="",labels=c("False posivite","True positive"))

mapq_phred.normal

pdf("~/Box Sync/Lab_work/Talks/2016_812/figures/mapq_phred.normal.pdf")
mapq_phred.normal
dev.off()

mapq_phred.stingy<-ggplot(subset(sig.df,category %in% c(T,F) & gc==5),aes(x=Phred,y=MapQ,color=category))+geom_point(alpha=1)+scale_x_continuous(limits=c(30,40))+geom_hline(yintercept=30)+geom_vline(xintercept=35)+scale_color_hue(name="",labels=c("False positive","True positive"))

mapq_phred.stingy

pdf("~/Box Sync/Lab_work/Talks/2016_812/figures/mapq_phred.stingy.pdf")
mapq_phred.stingy
dev.off()

@@

mapq_phred.roc<-ggplot(subset(h.cut.df,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.002))

mapq_phred.roc

pdf("~/Box Sync/Lab_work/Talks/2016_812/figures/mapq_phred.rocpdf")
mapq_phred.roc
dev.off()

@@

read.pos<-ggplot(subset(sig.cut.df,category %in% c(T,F) & gc==5),aes(x=Read_pos,fill=category))+geom_histogram(position='dodge')+scale_fill_hue(name="",labels=c("False positive","True positive"))+xlab("Average position on read")+ylab("Number of variants")
read.pos
pdf("~/Box Sync/Lab_work/Talks/2016_812/figures/read.pos.pdf")
read.pos
dev.off()

@@

read.roc<-ggplot(subset(h.cut.read.df,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.002))

read.roc

pdf("~/Box Sync/Lab_work/Talks/2016_812/figures/read.roc.pdf")
read.roc
dev.off()

@@

ac_freq<-ac_freq+geom_point(data=subset(medians,gc=="5"),mapping=aes(x=exp.freq,y=median),shape=95,size=30)
ac_freq

pdf("~/Box Sync/Lab_work/Talks/2016_812/figures/freq.pdf")
ac_freq
dev.off()

## Figure 5 Lower inputs
### 10^4
```{r,roc_lower_inputs4}
roc.4<-ggplot(subset(h.cut.read.df,gc==4),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.002))

roc.4

pdf("~/Box Sync/Lab_work/Talks/2016_812/figures/roc.4.pdf")
roc.4
dev.off()

@@

### 10^3
```{r,roc_lower_inputs3}
roc.3<-ggplot(subset(h.cut.read.df,gc==3),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.002))

pdf("~/Box Sync/Lab_work/Talks/2016_812/figures/roc.3.pdf")
roc.3
dev.off()

@@

dups.roc.p<-ggplot(dups.roc,aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.002))

dups.roc.p
pdf("~/Box Sync/Lab_work/Talks/2016_812/figures/dups.roc.pdf")
dups.roc.p
dev.off()

@@

This is so much better than before. 
### Concequences for diversity measurements
